%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Independent Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {JAVA Web-Socket application where the user uploads their own discord bot and host it on a dedicated machine.} % Role
    {\href{https://github.com/MattBelanger321/BotHostClient}{\dashuline{Discord Bot Host}}} % Project Name
    {July 2020} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {\textbf{Client} application implements \textbf{JAVA Swing} for an intuitive \textbf{GUI}.}
        \item {\textbf{Server} application uses \textbf{multi-threading} to allow for multiple bots to be hosted at once.}
        \item {\textbf{Server} application will \textbf{host} the bot automatically once it is received by the \textbf{client} application.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {JAVA application that modifies users Spotify playlists and queue.} % Role
    {\href{https://github.com/MattBelanger321/SpotifyApiExample}{\dashuline{Spotify App}}} % Project Name
    {April 2020} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implements the \textbf{\href{http://michaelthelin.se/spotify-web-api-java/}{\dashuline{Spotify Web Client API for JAVA}}} to give the user a quick and easy way to add songs to their queue.}
        \item {Input is prompted by an instinctive terminal interface for a quick and simple user experience. }
        \item{Utilizes an \textbf{automated authentication} process for quick access to the the main functionality of the program.}
      \end{cvitems}
    }
 %---------------------------------------------------------
 
  \cventry
    {A JAVA Server Client application used to grade C programs.} % Role
    {\href{https://github.com/MattBelanger321/CodeGrader}{\dashuline{Code Grader}}}
    {Mar. 2020} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A \textbf{JAVA} application where a \textbf{Windows client} sends a \textbf{C} program to a \textbf{Linux server} to be ran against test cases to generate a \textbf{submission report}.}
      \end{cvitems}
    }
   
%---------------------------------------------------------
  \cventry
    {Chess implemented in JAVA Swing.} % Role
    {\href{https://github.com/MattBelanger321/Chess}{\dashuline{Chess}}} % Project Name
    {Dec 2019} % Date
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implements a \textbf{graphical user interface} using the \textbf{JAVA Swing API} for an intuitive user experience.}
        \item {Uses \textbf{polymorphism} and \textbf{inheritance} to make the chess pieces.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Author/Mentor} % Role
    {\href{https://bennixmusic.github.io}{\dashuline{BennixMusic.com}}}  %Project Name
    {May 2020} % Date
    {}
    {
      \begin{cvitems} % Description(s)
        \item {Volunteer project to help a friend create website for his private business and to \textbf{teach} him basic \textbf{HTML/CSS}. Works on mobile and desktop.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
